\documentclass[10pt,letterpaper,sans]{moderncv}   % possible options include font size ('10pt', '11pt' and '12pt'), paper size ('a4paper', 'letterpaper', 'a5paper', 'legalpaper', 'executivepaper' and 'landscape') and font family ('sans' and 'roman')
% moderncv themes
\usepackage{perpage} %the perpage package
\MakePerPage{footnote} %the perpage package command
\moderncvstyle{classic}                        % style options are 'casual' (default), 'classic', 'oldstyle' and 'banking'
\moderncvcolor{black}                          % color options 'blue' (default), 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage[a4paper]{geometry}
\geometry{top=0.5in, bottom=0.4in, left=0.6in, right=0.6in}
\usepackage[most]{tcolorbox}
% personal data
\firstname{{\huge Berdakh}}
\familyname{{\huge Abibullaev, Ph.D.}}
\usepackage{framed}

\title{Curriculum Vitae}                     % optional, remove the line if not wanted
%\address{IEEE Senior Member \\2532 Yorktown Str, 22,\\ Houston, TX 77056 \\}{Permanent Resident, USA}
\address{IEEE Senior Member \\ 53 Qabanbay Batyr Avenue,\\}{Nur-Sultan, Kazakhstan}
% optional, remove the line if not wanted

\phone{+7~(771)~296~8074}                   % optional, remove / comment the line if not wanted
%\phone{+1~(832)~779~7737}
%\phone{ +7 (778) 437 4880}                      % optional, remove the line if not wanted
%\fax{+(82)-53-785-4659}                        % optional, remove the line if not wanted

\email{berdakh.abibullaev@nu.edu.kz}                  % optional, remove the line if not wanted
\extrainfo{https://nubmi.notion.site/}            % optional, draw the line if not wanted
%\photo[64pt][0.90pt]{profilephoto.jpg}

\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother
\begin{document}
\makecvtitle 
%\section{Research Interests}
%\vspace{-0.4cm}
%\cvitem{}{
%\begin{itemize}
%\item Brain-Computer/Machine Interface Systems researcher with deep expertise in analyzing time series data (i.e., EEG, ECoG, MEG, NIRS) for a real-time/offline pattern recognition. 
%\item Deep expertise in developing machine learning and deep learning systems to large-scale, real-world problems, and working with complex data to produce innovative analysis and predictive models for inference.
%\item Contribution to research communities and/or efforts, advance the state-of-the-art in the field, including generating patents and publications in top journals and conferences.
%\end{itemize}
%}
\section{Research Area}
\cvitem{}{\textbf{Neural Engineering:}
Brain-Computer/Machine Interfaces; EEG/MEG/ECoG/fNIRS signal processing.}
\cvitem{}{\textbf{Machine Learning:} Neural Networks and Deep Learning, Kernel based learning, Support vector machines.}
\vspace{-2pt}
\section{Education}
\cventry{02/2010}{Ph.D}{Yeungnam University}{Department of Electronic Engineering}{South Korea}{
\begin{itemize}
%\item \textit{Dissertation Topic}: "Epileptic Seizure Detection using Continuous Wavelet Transforms and Artificial Neural Networks".
%\item \textit{Academic advisor}: Professor Hee-Don Seo
\item \textit{Research area} : EEG time-series prediction, Machine learning and Neural Networks;
\end{itemize}} 
%-----------------------------------------------------------------
\cventry{08/2006}{M.Sc}{Yeungnam University}{Department of Electronic Engineering}{South Korea}{
\begin{itemize}
%\item \textit{Thesis Topic}: "Characteristic wave detection in ECG using complex-valued wavelet transforms".
%\item \textit{Academic advisor}: Professor Hee-Don Seo
\item \textit{Research area}: Wavelet Analysis, Time-frequency localization; Physiological feature extraction;
\end{itemize}
}  
%-----------------------------------------------------------------
\cventry{07/2004}{B.Sc}{Tashkent University of Information Technologies}{}{Uzbekistan}{}

\section{Academic Work Experience}
\cventry{08/2022-present}{Associate Professor}{Robotics \& Mechatronics Department, School of Engineering and Digital Science, Nazarbayev University}{Nur-Sultan, Kazakhstan}{}{}
\cventry{09/2015-08/2022}{Assistant Professor}{Robotics \& Mechatronics Department, School of Engineering and Digital Science, Nazarbayev University}{Nur-Sultan, Kazakhstan}{}
{{\begin{itemize}%
\item[Research Focus:] 
\item Deep learning algorithms for Brain-Computer/Machine Interfaces. 
\item Brain-Computer/Machine Interfaces in Neural-Rehabilitation after Stroke. 
\item Transfer learning applications in session/subject independent Brain-Computer/Machine Interfaces. 
\item High-Level Robotic Manipulator Control via Brain-Computer Interfaces for Assistive Applications  
\end{itemize}
}}

\cventry{5/2018 - 7/2018}{Visiting Professor}{Department of Electrical Engineering \& Computer Science, University of Houston}{Houston, Texas, USA}{}
%---------------------------------------------------------------------
{{\begin{itemize}                         
            \item Cortical source imaging of electroencephalographic signals in patients with stroke to examine neural correlates brain plasticity pre and post clinical trials with BMI. actuated exoskeleton.
        \end{itemize}
}} 


\cventry{9/2014 - 9/2015}{NIH Postdoctoral Research Fellow II}{Department of Electrical Engineering \& Computer Science, University of Houston}{Houston, Texas, USA}{}
%---------------------------------------------------------------------
{{\begin{itemize} 
            \item BMI-Exo Project: Brain-Machine Interface Control of a Therapeutic Exoskeleton for Neurorehabilitation.  
            \begin{itemize}
                \item Estimating neural correlates and mechanisms of an external command (mental intent) used to drive the external therapeutic exoskeleton for BMI.
            \end{itemize}
            \vspace{3pt}
            \item Neural Correlates of Infant Mirror Neuron System 
            \begin{itemize}
                \item Investigate the role the mirror neuron system plays in the motor learning of young infants via noninvasively acquired brain signals; 
                \item Categorizations of large-scale brain connectivity analysis to understand neural mechanisms of infant behavior.
            \end{itemize}
            \item Electromagnetic-source localization and estimating brain network in connectivity analysis 
        \end{itemize}
    }}\vspace{10pt}

\cventry{01/2014-09/2014}{Research Scientist}{Department of Neurology, Samsung Medical Center}{Seoul, South Korea}{}
%---------------------------------------------------------------------
{{\begin{itemize} 
\item Investigated High-Frequency Oscillations of ECoG/EEG signals relevant to Epileptogenesis using machine learning algorithms. Supported medical doctors through brain data analysis in the presurgical evaluation of patients with refractory epilepsy.
\item Neuroelectromagnetic source localization from scalp EEG \& MEG recordings for delineation of epileptogenic zones in the surgical treatment of refractory focal epilepsy.
\end{itemize}
}} 


\cventry{04/2011-12/2013}{Senior Research Scientist}{Robotics Research Division, Daegu Gyeongbuk Institute of Science and Technology}{South Korea}{}
{Development of rehabilitation strategies for stroke patients via robot-assisted physical therapy with BCIs.
{\begin{itemize}%
\item Implemented kernel-based machine learning algorithms for online BCIs to control neuro-rehabilitation devices. 
\item Examined inter-subject/session variabilities to enhance fNIRS-based BCI performances. 
\item Design and optimization of non-invasive based BCI paradigms for real-time robot control. 
\end{itemize}
}} 
 
\cventry{01/2010-04/2011}{Postdoctoral Research Scholar}{Robotics Research Division, Daegu Gyeongbuk Institute of Science and Technology}{South Korea}{}{
{Brain-Computer Interfaces in therapy and diagnosis of Attention Deficit and Hyperactivity Disorders (ADHD). 
\begin{itemize}%
\item Involved in quantitative EEG and Neurofeedback methods of ADHD children. Time-frequency localization; Identification of strongly relevant neural signal patterns of ADHD using machine learning. 
\item Developed machine learning-based semi-supervised feature selection and classification algorithms. 
\item Participated in the developmental assessment of ADHD children during a long-term neuro-therapy in cooperation with a neurorehabilitation center at Daegu University.
\end{itemize}
}} 

\section{Honors and Awards}
\cvitem{11/2017}{Best paper award: \textit{fNIRS motion artifact correction for overground walking using entropy-based unbalanced optode decision and wavelet regression neural network},'' in Multisensor Fusion and Integration for Intelligent Systems, 2017 IEEE International  Conference.}
\cvitem{06/2014}{Best poster award on "\textit{The evaluation of accuracy and clinical usefulness of 3D EEG source localization analysis}," Korean Epilepsy Congress 2014.}
\cvitem{12/2012}{Best Researcher of the Year Award. Robotics Research Division, Daegu Gyeongbuk Institute of Science and Technology, Daegu, South Korea.}
\cvitem{01/2011}{Enlisted in Marquis Who's Who in the World 2011, 28th Edition, USA}
\cvitem{09/2006}{Korean Government Information Technology Scholarship for International Graduate Students for the Ph.D. program, South Korea.}
\cvitem{09/2004}{Brain Korea \#21 Scholarship for the MSc program.}
 

\section{Technical Skills}
\cventry{}{Software skills}{}{}{}{
{Expert in the Python language and libraries such as Cython; very good knowledge of C, C++. Experience with various tools and languages, including bash, LATEX, HTML, Git, and different database query languages. }}

\cventry{}{Data Science}{}{}{}{
{Expert knowledge in NumPy, Scipy, Pandas, Sklearn, PyTorch Deep larning libraries}}

%-------------------------------------------------------------------------
\cventry{}{Neural data acquisition systems}{}{}{}{
{Expertise with Nicolet EEG Amplifiers, Blackrock Microsystems (intracranial recording), Functional Near-Infrared Spectroscopy FOIRE3000, BIOPAC fNIR200 Optical Brain Imaging, BioSemi Active-Two EEG system, Brain Products EEG amp., BIOPAC MP100 EEG amp. And G.tec g.USBamp systems. }}

\cventry{}{Productivity applications}{}{}{}{
{\TeX : [\LaTeX, BibTEX, PSTricks, Beamer].}}
\cventry{}{System Environments}{}{}{}{{Linux (Pop\!\_OS, Ubuntu), Windows}}
\vspace{5pt}
 
\section{Service to the Scientific Community}
\cventry{}{Associate Editor}{}{}{}{
    {\begin{itemize}%
            \item IEEE Access Journal (Impact Factor: 3.7)
            \item PeerJ Computer Science (Impact Factor: 3.09)
    \end{itemize}
}}

\cventry{}{Occasional Reviewer}{}{}{}{
{\begin{itemize}%
        \item IEEE Access Journal
        \item Neuroimage, Elsevier.
        \item IEEE Transactions on Neural Networks and Learning Systems
        \item Brain Research, Elsevier.
    \end{itemize}
}}

\cventry{}{Program Committee Member and Session Chair}{}{}{}{
{\begin{itemize} 
        \item International Workshop on Artificial Intelligence for Healthcare Applications at International Conference on Pattern Recognition 2020. 
        \item Session Chair: The 6th International Conference on Brain-Computer Interface (BCI), IEEE, 2018, South Korea.
        \item Session Chair: IEEE International Conference on Multisensory Fusion and Integration for Intelligent Systems, 2017, Daegu, South Korea.        
        \item Session Chair: International Conference on Control Automation and Systems Oct.27-30, 2010, Seoul, South Korea
    \end{itemize}
}}

\section{Project Proposals, Participation \& Coordination}
\cventry{01/2021}{Principal Investigator}{\textbf{Brain-Machine Interfaces for Neural Rehabilitation after Stroke}}{}{This project aims to accelerate the efficacy of robotic rehabilitation using a new neural interface system developed for upper-limb repair after stroke. It aims to facilitate expediate motor recovery from incomplete upper-limb paralysis and investigate in-depth understanding of cortical reorganization in the brain associated with the recovery.}{} 

\cventry{01/2021}{Co-Investigator}{\textbf{Classifier Validity and Its Applications in Bioinformatics}}{}{The project studies the measures of classifier validity and explores their applications in bioinformatics. Nazarbayev University.}{} 

\cventry{01/2019}{Co-Investigator}{\textbf{Neural-assisted optimization of human learning with multimodal neuroimaging of EEG and NIRS}}{}{Implementing and validate a neural-assisted, machine-learning-based intelligent  tutoring system that uses information from physiological signals to adapt the learning schedule to a user's individual learning capacity.}{} 

\cventry{09/2015}{Principal Investigator}{\textbf{Development of a Brain-Computer Interface with a Robot and Functional-Electrical Stimulation for Upper-Limb Stroke Rehabilitation (BCI-ROBOFES)}}{}{Evaluated by the committee of Oak Ridge Associated Universities (ORAU);}{} 

\cventry{9/2014}{Participant}{Cognitive-Motor Development Research in Infants.}{}{Lead a team of Ph.D. students in exploring \& decoding of the neural basis of \textit{Imitation and Action Understanding} in freely-behaving infants via multimodal brain imaging techniques, University of Houston, Texas}{} 

\cventry{9/2014}{Participant}{\textbf{The BMI-Exo Project: Facilitating Personalized Robotic Rehabilitation Of The Upper Limb, [NIH Grant R01NS081854-02, National Robotics Initiative]}}{}{Lead a part of research that focuses on understanding neurophysiological correlates of motor learning during    movements in stroke patients.}{} 

\cventry{04/2014}{Participant}{\textbf{Development of high-resolution subdural electrodes and data mining methods for precise localization of epileptogenic zone in treatment of patients with refractory epilepsy.}}{}{Participated in idea generation and in drafting/writing of the project proposal at Samsung Medical Center, Korea}{} 

\vspace{0.5cm}

\section{Publications}
\renewcommand{\refname}{Patents}
\begin{thebibliography}{10}
    \small
    \bibitem{p1}
    J.~An, S.H.~Jin, S.H.~Lee, J.I.~Moon  \underline{B. Abibullaev}, J.H.~Ahn and G.H. Jang.
    \newblock \textbf{Rehabilitation Training System and Method}.
    \newblock {\em U.S. Patent No}: 9,081,890,Washington, DC: United States. Patent and Trademark Office, 2015 (https://www.google.com/patents/US9081890).
    %------------------------------
    \bibitem{p2}
    J.~An, S.H.~Jin, S.H.~Lee, J.I.~Moon  \underline{B. Abibullaev}, J.H.~Ahn and G.H. Jang.
    \newblock \textbf{Self-directed rehabilitation training method combining brain signals and functional electro-stimulation}.
    \newblock {\em EFS ID}: 17077057, 09-OCT-2013, United States, (http://www.google.com/patents/US20140200632).
    \bibitem{k1}
    J. An, S.H. Jin, S.H. Lee, \underline{B. Abibullaev}, J.I. Moon , J.H. Ahn and G.H. Jang. \newblock \textbf{Combining Brain Signals and Functional Electrostimulation Self-Directed Rehabilitation Method}, \newblock Patent Registration Number: 101501524000, 05.03.2015. South Korea,(http://eng.kipris.or.kr/). 
\end{thebibliography}

\vspace{12pt}
\renewcommand{\refname}{Refereed Journal Publications}  

\label{publication}
\begin{thebibliography}{10}
    \small 
    \bibitem{haa1aa}
    \underline{B. Abibullaev}, Kassymzhomart Kunanbayev and A. Zollanvari,
    \newblock \textbf{Subject-Independent Classification of P300 Event-Related Potentials Using a Small Number of Training Subjects},
    \newblock \textit{IEEE Transactions on Human-Machine Systems}, DOI: 10.1109/THMS.2022.3189576, 2022.(https://doi.org/10.1109/THMS.2022.3189576)\textit{(\textbf{Impact Factor: 4.124}; Quartile rank: Q1)}.

    \small 
    \bibitem{haa1aax}
    I. Dolzhikova, \underline{B. Abibullaev}, R. Sameni  and A. Zollanvari,
    \newblock \textbf{Subject-Independent Classification of Motor Imagery Tasks in EEG using Multi-Subject Ensemble CNN},
    \newblock \textit{IEEE Access}, DOI: 10.1109/ACCESS.2022.3195513, 2022.(https://doi.org/10.1109/ACCESS.2022.3195513)\textit{(\textbf{Impact Factor: 3.476}; Quartile rank: Q1)}.
    
    \small 
    \bibitem{haa21}
    \underline{B. Abibullaev} and A. Zollanvari,
    \newblock \textbf{A Systematic Deep Learning Model Selection for P300-Based Brain-Computer Interfaces},
    \newblock \textit{IEEE Transactions on Systems, Man, and Cybernetics: Systems}, DOI: 10.1109/TSMC.2021.3051136, 2021.(https://ieeexplore.ieee.org/document/9351887)\textit{(\textbf{Impact Factor: 13.451}; Quartile rank: Q1)}.

    \small 
    \bibitem{haa31}
    A. Zollanvari and \underline{B. Abibullaev}
    \newblock \textbf{Bias Correction for Linear Discriminant Analysis},
    \newblock \textit{Pattern Recognition Letters}, vol. 151, pp. 41-47, 2021, https://doi.org/10.1016/j.patrec.2021.07.026 \textit{(Impact Factor: 3.7; Quartile rank: Q1)}.
 
    \small 
    \bibitem{haa41}
    \underline{B. Abibullaev} and A. Zollanvari,
    \newblock \textbf{Learning Discriminative Spatiospectral Features of ERPs for Accurate Brain-Computer Interfaces}
    \newblock \textit{IEEE Journal of Biomedical and Health Informatics}, vol. 98, pp. 1-12, 2019, DOI: 10.1109/JBHI.2018.2883458 \textit{(Impact Factor: 5.772; Quartile rank: Q1)}.

    \small 
    \bibitem{haa412}
    \underline{B. Abibullaev}, I. Dolzhikova and A. Zollanvari, 
    \newblock \textbf{A Brute-force CNN Model Selection for Accurate Classification of Sensorimotor Rhythms in BCIs} \newblock \textit{IEEE Access}, 2020,  DOI: 10.1109/ACCESS.2020.2997681
    \textit{(Impact Factor: 3.36; Quartile rank: Q1)}.


    \small 
    \bibitem{ha3a12}
    \underline{B. Abibullaev}, A. Zollanvari, B. Saduanov and T. Alizadeh, 
    \newblock \textbf{Design and Optimization of a BCI-Driven Telepresence Robot Through Programming by Demonstration}
    \newblock \textit{IEEE Access}, August 2019,  DOI: 10.1109/ACCESS.2019.2933268
    \textit{(Impact Factor: 3.36; Quartile rank: Q1)}.

    \small 
    \bibitem{h3aa12}
    A. Zollanvari,  M. Abdirash, A. Dadlani and \underline{B Abibullaev}.
    \newblock \textbf{Asymptotically Bias-Corrected Regularized Linear Discriminant Analysis for Cost-Sensitive Binary Classification}
    \newblock \textit{IEEE Signal Processing Letters}, 22 May 2019,  DOI: 10.1109/LSP.2019.2918485 \textit{(Impact Factor: 3.1; Quartile rank: Q1)}.
        
    \small 
    \bibitem{ha1}
    \underline{B. Abibullaev}, J An, SH Lee, JI Moon.
    \newblock \textbf{Design and Evaluation of Action Observation and Motor Imagery based {BCIs} using {NIRS}} \newblock \textit{Measurement},vol. 98, pp. 250-261, 2017, Elsevier \textit{(Impact Factor: 3.927; Quartile rank: Q1)}.
    
    \small
    \bibitem{hay1}
    N.A. Bhagat, A. Venkatakrishnan, \underline{B. Abibullaev}, E.J. Artz, N. Yozbatiran, A. Blank, J. French, C. Karmonik, R.G.Grossman, M.K O'Malley, G. Francisco, J.L. Contreras-Vidal.
    \newblock \textbf{Design and optimization of an {EEG}-based brain-machine interface (BMI) to an upper-limb exoskeleton for stroke survivors.}
    \newblock {\em Frontiers in Neuroscience}, vol. 10, March, 2016 (Impact Factor: 4.677; Quartile rank: Q1).
    
    \small
    \bibitem{h221}
    J.G. Cruz-Garza, Z.R. Hernandez, T. Tse, E. Caducoy, \underline{B. Abibullaev}, J.L. Contreras-Vidal.
    \newblock \textbf{A novel experimental and analytical approach to the multimodal neural decoding of intent during social interaction in freely-behaving human infants.}
    \newblock {\em Journal of Visualized Experiments}, DOI: 10.3791/53406, October, 2015 (Impact Factor : 1.5; Quartile rank: Q2).
    
    \small
    \bibitem{h3}
    C.H. Park, J.H Seo, D. Kim, \underline{B. Abibullaev}, H. Kwon, Y.H. Lee, M.Y. Kim, K. Kim, J.S. Kim, E.Y. Joo, S.B. Hong, (2015, Feb). 
    \newblock \textbf{{EEG} Source Imaging in Partial Epilepsy in Comparison with Presurgical Evaluation and Magnetoencephalography.}
    {\em Journal of Clinical Neurology}, 2015 Feb 17, 11:e12 (Impact Factor : 3.077; Quartile rank: Q2).
    
    \bibitem{ha}
    \underline{B. Abibullaev}, J~An, S.H.~Jin, and J.I.~Moon.
    \newblock \textbf{Classification of brain hemodynamic signals arising from
    visual action observation tasks for brain-computer interfaces : An {fNIRS} study. }\newblock {\em Measurement}, \newblock {DOI:10.1016/j.measurement.2013.11.044}, 2014. Elsevier (Impact Factor : 3.927; Quartile rank: Q1).
    %------------------------------
    \bibitem{hb}
    \underline{B. Abibullaev}, J~An, S.H.~Lee, S.H.~Jin, and J.I.~Moon.
    \newblock \textbf{Minimizing inter-subject variability in {fNIRS} based brain computer interfaces via multiple-kernel support vector learning.}
    \newblock {DOI: 10.1016/j.medengphy.2013.08.009,} {\em Medical Engineering Physics}, 2013. Elsevier (Impact Factor : 2.242; Quartile rank: Q2).
    %------------------------------
    \bibitem{a}
    \underline{B. Abibullaev} and J.~An.
    \newblock \textbf{Classification of frontal cortex hemodynamic response during cognitive tasks using wavelet transforms and machine learning algorithms.}
    \newblock {\em Medical Engineering Physics}, 34(10):1394--410, 2012. Elsevier (Impact Factor : 2.242; Quartile rank: Q2).
    
    \bibitem{c}
    \underline{B. Abibullaev} and J.~An.
    \newblock \textbf{Decision support algorithm for diagnosis of {ADHD} disorder using electroencephalograms.}
    \newblock {\em Journal of Medical Systems}, 36(4):2675--2688, 2011. Springer (Impact Factor : 4.460; Quartile rank: Q2).
    
    \bibitem{b}
    \underline{B. Abibullaev}, J.~An, and J.I. Moon.
    \newblock \textbf{Neural network classification of brain hemodynamic responses from four mental tasks.} \newblock {\em Int J Optomechatronics}, 5(4):340--359, 2011. Taylor \&  Francis (Impact Factor : 1.9; Quartile rank: Q2).
    
    \bibitem{d}
    \underline{B. Abibullaev} and H.D. Seo.
    \newblock \textbf{A new {QRS} detection method using wavelets and artificial neural networks.} \newblock {\em Journal of Medical Systems}, 35(4):683--691, 2011. Springer (Impact Factor : 4.460; Quartile rank: Q2).
    
    \bibitem{e}
    \underline{B. Abibullaev}, M.S. Kim, and H.D. Seo.
    \newblock \textbf{Epileptic spike detection using continuous wavelet transforms and artificial neural networks.} \newblock {\em Int J of Wavelets, Multires and Inform Proc}, 8(1):33--48, 2010.  Worldscientific (Impact Factor : 0.463; Quartile rank: Q3).
    
    \bibitem{f}
    \underline{B. Abibullaev}, M.S. Kim, and H.D. Seo.
    \newblock \textbf{Seizure detection in temporal lobe epileptic {EEGs} using the best basis wavelet functions.} \newblock {\em Journal of Medical Systems}, 34(4):755--765, 2010. Springer (Impact Factor : 4.460; Quartile rank: Q2).
    
    \bibitem{g}
    M.S. Kim, Y.C. Cho, \underline{B. Abibullaev}, and H.D. Seo.
    \newblock \textbf{Analysis of brain functions and classification of sleep stage {EEG} using daubechies wavelet.} \newblock {\em Sensors and Materials}, 20(1):1--15, 2008. MYU, Japan (Impact Factor: 0.92; Quartile rank: Q3).

\end{thebibliography}
\vspace{0.2cm}

    
\renewcommand{\refname}{Conference proceedings}
\begin{thebibliography}{10}
\bibitem{ict1wa}
\small
V. Mun And \underline{B.~Abibullaev}, "\textbf{Explainable Deep Learning for Brain-Computer Interfaces through Layerwise Relevance Propagation}", 2023 11th International Winter Conference on Brain-Computer Interface (BCI), 2023, pp. 1-5, doi: 10.1109/BCI53720.2022.9734904.

    
\bibitem{ict1w}
\small
I. Dolzhikova, \underline{B.~Abibullaev}, A. Zollanvari, "\textbf{An Ensemble of Convolutional Neural Networks for Zero-Calibration ERP-Based BCIs}", 2022 10th International Winter Conference on Brain-Computer Interface (BCI), 2022, pp. 1-4, doi: 10.1109/BCI53720.2022.9734904.
  
\bibitem{ict1}
\small
I. Dolzhikova, \underline{B.~Abibullaev}, R. Sameni, A. Zollanvari, "\textbf{An Ensemble CNN for Subject-Independent Classification of Motor Imagery-based EEG}", the 43rd Annual International Conference of the IEEE Engineering in Medicine and Biology Society (EMBS), October 31 – November 4, 2021
\bibitem{ict2}
\small
Y. Kainolda, \underline{B.~Abibullaev}, R. Sameni, A. Zollanvari, "\textbf{Is Riemannian Geometry Better than Euclidean in Averaging Covariance Matrices for CSP-based Subject-Independent Classification of Motor Imagery?}", the 43rd Annual International Conference of the IEEE Engineering in Medicine and Biology Society (EMBS), October 31 – November 4, 2021
\bibitem{ict3}
\small
M. Nurpeiissov, \underline{B.~Abibullaev}, T. Alizadeh,  "\textbf{A novel human-robot interaction framework based on Telegram and programming by demonstration}", 9th International Conference on Robot Intelligence Technology and Applications (RITA 2021), on Dec 16 -- 17, 2021 at KAIST Daejeon, Korea.
    
\bibitem{ict}
\small
S. Abilkassov, M. Kairgaliyev, B. Zhakanov, \underline{B.~Abibullaev}, 
"\textbf{A System For Drivers' Cognitive Load Estimation Based On Deep Convolutional Neural Networks and Facial Feature Analysis}", in 22nd IEEE International Conference on Industrial Technology, Virtual 10-12, 2021, Spain.

\bibitem{bci21}
\small
K. Kunanbayev, \underline{B.~Abibullaev}, A. Zollanvari, "\textbf{Data Augmentation for P300-based Brain-Computer Interfaces Using Generative Adversarial Networks}", in 2021 9th International Winter Conference on Brain-Computer Interface (BCI), 22-24 Feb. 2021, pp. 1-7, Gangwon, Korea (South), doi: 10.1109/BCI51272.2021.9385317.

\bibitem{bci211}
\small
K. Kunanbayev, D. Azhigulov,  \underline{B.~Abibullaev}, A. Zollanvari, "\textbf{Deep Transfer Learning for Subject-Independent ERP-based BCIs}", in 2021 9th International Winter Conference on Brain-Computer Interface (BCI), 22-24 Feb. 2021, pp. 1-3,  Gangwon, Korea (South), doi: 10.1109/BCI51272.2021.9385311.

\bibitem{bcn22}
\small
A. Oleinikov, \underline{B.~Abibullaev}, M. Folgheraiter, "\textbf{On the Classification of 
Electromyography Signals to Control a Four Degree-Of-Freedom Prosthetic Device},"
in 2020 42nd Annual International Conference of the IEEE Engineering in Medicine \& 
Biology Society (EMBC), July 20-24, Montreal, Canada. 

\bibitem{bciii}
\small
B. Saduanov, D. Tokmurzina, K. Kunanbayev and \underline{B.~Abibullaev}, "\textbf{Design and 
Optimization of a Real-Time Asynchronous BCI Control Strategy for Robotic Manipulator 
Assistance}", in 2020 8th International Winter Conference on Brain-Computer Interface. 
(BCI), 2020, GangWon, South Korea. 

\small
\bibitem{NER2019}
Adilet Tuleuov and \underline{B.~Abibullaev}, ``\textbf{Deep Learning Models for Subject-Independent ERP-based Brain-Computer Interfaces},'' in
\emph{the 2019 9th International IEEE/EMBS    Conference on Neural Engineering (NER)}, March 20-23, 2019, San Francisco, CA, USA.

\bibitem{bci2019}
\underline{B.~Abibullaev}, Y. Orazayev, and A. Zollanvari, ``\textbf{Novel Spatiospectral Features of ERPs Enhances Brain-Computer Interfaces},'' in \emph{Brain-Computer Interface (BCI), 2019
    7th International Conference on}.\hskip 1em plus 0.5em minus 0.4em\relax
IEEE Brain Society, 2019, GangWon, South Korea.

\small
\bibitem{saduanov2018brain}
    B.~Saduanov, D.~Tokmurzina, T.~Alizadeh, and \underline{B.~Abibullaev}, ``\textbf{Brain-computer interface humanoid pre-trained for interaction with people},'' in
    \emph{2018 ACM/IEEE International Conference on Human-Robot Interaction}.\hskip 1em plus 0.5em minus 0.4em\relax ACM, March 5-8, 2018, pp. 229--230, Chicago, IL, USA.

\small    
\bibitem{oleinikov2018feature}
    A.~Oleinikov, \underline{B.~Abibullaev}, A.~Shintemirov, and M.~Folgheraiter, ``\textbf{Feature  extraction and real-time recognition of hand motion intentions from emgs via
    artificial neural networks},'' in \emph{Brain-Computer Interface (BCI), 2018
        6th International Conference on}.\hskip 1em plus 0.5em minus 0.4em\relax
    IEEE Brain Society, 2018, pp. 1-5, GangWon, South Korea.

\small 
\bibitem{bci2018}
G. Lee, S. H. Jin, S. T. Yang, J. An, and \underline{B.~Abibullaev}, "\textbf{Cross-correlation between HBO and HbR as an effective feature of motion artifact in the fNIRS signal}," 2018 6th International Conference on Brain-Computer Interface (BCI), pp. 1-3, 2018, IEEE Brain Society, GangWon, South Korea.


\small 
\bibitem{saduanov2018trained}
B.~Saduanov, T.~Alizadeh, J.~An, and \underline{B.~Abibullaev}, ``\textbf{Trained by demonstration
humanoid robot controlled via a BCI system for telepresence},'' in
\emph{Brain-Computer Interface (BCI), 2018 6th International Conference on}.\hskip 1em plus 0.5em minus 0.4em\relax IEEE Brain Society, 2018, pp. 1--4, January, GangWon, South Korea.

\small 
\bibitem{lee2017fnirs}
G.~Lee, S.~H. Jin, S.~H. Lee, \underline{B.~Abibullaev}, and J.~An, ``\textbf{fNIRS motion artifact correction for overground walking using entropy-based unbalanced optode decision and wavelet regression neural network},'' in \emph{Multisensor Fusion and Integration for Intelligent Systems (M.F.I.), 2017 IEEE International Conference on}.\hskip 1em plus 0.5em minus 0.4em\relax IEEE, 2017, pp. 186--193, Daegu, South Korea.

\small
\bibitem{h2a010}
A. Zhumadilova, D. Tokmurzina, A. Kuderbekov, and \underline{B. Abibullaev}.
\newblock \textbf{ Design and Evaluation of a {P300} Visual Brain-Computer Interface Speller in Cyrillic Characters}. \newblock In \textit{the 26th IEEE International Symposium on Robot and Human Interactive Communication (RO-MAN), IEEE}, 2017, Aug 28 - Sept 1, Lisbon, Portugal.

\small
\bibitem{h2a01}
\underline{B. Abibullaev}.
\newblock \textbf{Learning Suite of Kernel Feature Spaces Enhances SMR-Based {EEG}-{BCI} Classification.} \newblock In \textit{the 5th International Winter Conference on Brain-Computer Interface, IEEE}, 2017, January 9-11, GangWon, South Korea.

\small
\bibitem{h2a0}
D. Nurseitov, A. Serekov, A. Shintemirov and \underline{B. Abibullaev}.
\newblock \textbf{Design and Evaluation of a {P300}-{ERP} based {BCI} System for Real-Time Control of a Mobile Robot.} \newblock In \textit{the 5th International Winter Conference on Brain-Computer Interface, IEEE}, 2017, January 9-11, Gangwon , South Korea.

\small
\bibitem{h2a1}
\underline{B. Abibullaev} and J An. 
\newblock \textbf{On Robust Classification of Hemodynamic Signals for {BCI}s via Multiple Kernel $\nu$-SVMs.}
\newblock \textit{Intelligent Robots and Systems (IROS), 2016 IEEE/RSJ International Conference}, 2016, Oct10-15, Daejeon, South Korea.

\small
\bibitem{h2}
J.G. Cruz-Garza, Z.R. Hernandez, M. Megjhani, \underline{B. Abibullaev}, T. Tse, E. Caducoy, and JL Contreras-Vidal.
\newblock \textbf{Neural Development of social cognition in the first two years of life - Early findings.}
\newblock In {\em Society for Neuroscience} 2015 Oct 17-21; Chicago, USA.

\bibitem{h3}
Z.R. Hernandez, A.J. Arenas-Castellanos, J.G. Cruz-Garza, M. Megjhani, \underline{B. Abibullaev}, Sri. R.P. Maddi, T. Tse,  C. Armstrong, W. Long, J.L. Contreras-Vidal
\newblock \textbf{Decoding Intent From Non-invasive {EEG} in Freely Behaving Infants.}
\newblock In {\em Ninth Biennial Meeting of the Cognitive Development Society} 2015 Oct 9-10; Ohio, U.S.A.

\bibitem{haax1}
A.J. Arenas-Castellanos, Z.R. Hernandez, J.G. Cruz-Garza, M. Megjhani, \underline{B. Abibullaev}, Sri. R.P. Maddi, T. Tse,  C. Armstrong, W. Long, J.L. Contreras-Vidal
\newblock \textbf{A developmental Analysis of Behaviors Related to the Mirror Neuron System in 6-24 Months Infants}
\newblock In {\em Ninth Biennial Meeting of the Cognitive Development Society} 2015 Oct 9-10; Ohio, U.S.A.

\bibitem{cP2015}
Z.R. Hernandez, J.G. Cruz-Garza, T. Tse, E. Caducoy, \underline{B. Abibullaev}, J.L. Contreras-Vidal.
\newblock \textbf{Supervised Classification of Intended Behaviors Using Electroencephalography ({EEG}) from Freely-Behaving Infants: Early Findings.}
\newblock In {\em 12th Annual G.C.C. Conference on Theoretical and Computational Neuroscience}, Rice University, Houston, TX, United States, February 6-7, 2015.

\bibitem{Bhagat2015}
N. A. Bhagat, A Venkatakrishnan, \underline{B. Abibullaev}, E. J. Artz, A.A. Blank, J. A. French, N. Yozbatiran, and R. G. Grossman, M. K. O'Malley, J. L. Contreras-Vidal, G. E. Francisco
\newblock \textbf{{BMI} Control of a Therapeutic Exoskeleton to Facilitate Personalized Robotic Rehabilitation of the Upper Limb.} 
\newblock {\em In National    Robotics Initiative    (N.R.I.) P.I. Meeting}, Westin Arlington, Nov. 19-20 2014, United States.  

\bibitem{cP2014}
C.H.Park,  \underline{B. Abibullaev}, E.Y.~Joo, S.C. Hong and S.B. Hong.
\newblock \textbf{The evaluation of accuracy and clinical usefulness of 3D {EEG} source localization analysis.}
\newblock In {\em the 19th Korean Epilepsy Congress}, Seoul, Republic of Korea, June 12-14 2014.

\bibitem{aP2013}
S.H. Lee, J.~An, G.~Jang, S.H. Jin, \underline{B. Abibullaev}, and J.I. Moon.
\newblock \textbf{Neural activity during observation, imagery, and execution of eating: An {fNIRS} pilot study.}
\newblock In {\em the 19th Annual Meeting of the Organization for Human Brain
  Mapping}, Seattle, WA, United States, June 16-20, 2013.

\bibitem{absadddd2013}
J.~An, S.H. Jin, S.H. Lee, G.~Jang, \underline{B. Abibullaev}, J.~Ahn, H.~Lee, and J.I. Moon.
\newblock \textbf{Cortical activation pattern for grasping during observation, imagery, execution, {FES}, and observation-{FES} integrated {BCI}: An {fNIRS} pilot study.}
\newblock In {\em the 35th Annual Int. Conference of the {IEEE} Engineering in Medicine and Biology Society (EMBC)}, Osaka, Japan, July 3-7 2013.

\bibitem{absa2013}
J.~An, S.H. Lee, S.H. Jin, \underline{B. Abibullaev}, G.~Jang, J.~Ahn, H.~Lee,  and J.I. Moon.
\newblock \textbf{The beginning of neurohaptics: Controlling cognitive interaction via brain haptic interface.}
\newblock In {\em the 2013 IEEE International Winter Workshop on Brain-Computer Interface}, Gangwon Province, Korea, Feb. 18-20 2013.

\bibitem{absas2012}
\underline{B. Abibullaev}, J.~An, J.I. Moon, S.H. Lee, and S.H. Jin.
\newblock \textbf{A study on the {BCI}-{Robot} assisted stroke rehabilitation framework using brain hemodynamic signals.}
\newblock In {\em the 9th Int Conference on Ubiquitous Robots and Ambient Intelligence}, IEEE proceedings, Daejon, Korea, November 26-29 2012.

\bibitem{absa22012}
\underline{B. Abibullaev}, J.~An, S.H.Lee, S.H. Jin, J.I Moon, H.J. Lee.
\newblock \textbf{Decoding of Hemodynamic Brain Responses for Brain-Computer Interfaces via Ensemble Support Vector Learning.}
\newblock In {\em the Human-Computer Interaction Conference}, Gangwon-Do, Korea, January 11-13, 2012.

\bibitem{adb2012}
\underline{B. Abibullaev}, W.S. Kang, S.H. Lee, J.~An, and H.D. Seo.
\newblock \textbf{Near-Infrared Spectroscopy in the analysis of functional brain activity during cognitive tasks.}
\newblock In {\em 2010 IEEE Sensors Conference}, Hawaii, United States, November 1-4, 2010.

\bibitem{asdsc2010}
\underline{B. Abibullaev}, W.S. Kang, S.H. Lee, and J.~An.
\newblock \textbf{Recognition of brain hemodynamic mental response for brain-computer interfaces.}
\newblock In {\em International Conference on Control Automation and Systems}, IEEE proceedings,  Gyeonggi-do, Korea, October 27-30 2010.

\bibitem{acd2010}
S.H. Lee, \underline{B. Abibullaev}, W.S. Kang, and J.~An.
\newblock \textbf{analysis of attention deficit hyperactivity disorder in {EEG} using wavelet transform and self-organizing maps.}
\newblock In {\em International Conference on Control Automation and Systems}, IEEE proceedings, Gyeonggi-do, Korea, October 27-30 2010.
%
\bibitem{aaag2010}
W.S. Kang, \underline{B. Abibullaev}, S.H. Lee, and J.~An.
\newblock \textbf{Path planning algorithm using the values clustered by K-means.}
\newblock In {\em the 15th Int. Symposium on Artificial Life and Robotics}, Japan, February 4-6, 2010.

\bibitem{ata2010}
\underline{B. Abibullaev}, H.D. Seo, W.S. Kang, and J.~An.
\newblock \textbf{A wavelet-based method for detecting and localizing epileptic neural spikes in {EEG} signals.}
\newblock In {\em the 2nd Int. Conf. on Interaction Sciences: Information Technology, Culture, and Human. A.C.M.}, Seoul, Korea,  Nov. 24- 26, 2009.

\bibitem{atda2010}
\underline{B. Abibullaev} and H.D. Seo.
\newblock \textbf{Epileptic seizures detection using continuous time wavelet based neural networks.}
\newblock In {\em the 6th International Conference on Information Technology: New Generations, IEEE Computer Society}, Las Vegas, Nevada, United States, April 27-29 2009.

\end{thebibliography}
\vspace{10pt}
%-------------------------------------------------------------------------
\section{Mentoriship}
\cvitem{}{\textbf{Current Students:}
\begin{itemize}
    \item Supervisor: Zhenis Otarbay, Ph.D. Student (1st year), Dissertation: "\textbf{Design and Evaluation of Brain-Machine Interfaces for Upper-limb Stroke Rehabilitation}" 
    \vspace{0.5cm}
    \item Co-Supervisor: Irina Fedorova, Ph.D. Student (3rd year), Supervisor: Prof. Amin Zollanvari, Dissertation: "\textbf{Robust Data-driven Predictive Models for Brain-Computer Interfaces}"\vspace{0.5cm}
    \item Co-Supervisor: Inara Tusseyava, Ph.D. Student (3rd year), Supervisor: Prof. Matteo Rubagotti, Dissertation: "\textbf{Perceived Safety in Human-Robot Interaction}"\vspace{0.5cm}    
    \item Supervisor: Kuanysh Kudaibergenov, M.Sc. Student (2nd year), Thesis: \textbf{"Subject to Subject Transfer Learning for BCIs using Deep Transformers Networks"}\vspace{0.5cm}
    \item Supervisor: Kulyan Karipbayeva, M.Sc. Student (2nd year), Thesis: "\textbf{Non-Invasive Brain-Computer Interfaces for Speech Synthesis}"\vspace{0.5cm}
    \item Supervisor: Aigerim Keutayeva, M.Sc. Student (1st year), Thesis: "\textbf{Robust Subject Independent BCIs using Attention Mechanism based CNNs}"\vspace{0.5cm} 
    \item Co-Supervisor: Vladislav Mun, M.Sc. Student (2nd year), Co-Supervisor: Prof. Siamac Fazli, Thesis: "\textbf{Explainable Deep  Learning for Brain-Computer Interfaces}"\vspace{0.5cm}
\end{itemize}
}
\cvitem{}{\textbf{Past Students:} 
\begin{itemize}
    \item Supervisor: Alen Kabdislam, M.Sc. Student (June 2020), Thesis: "\textbf{EEG Decoding and Classification using Deep Learning with Convolutional Neural Networks}" (currently Senior Data Scientist at First Heartland Jusan Bank)\vspace{0.5cm}
    \item Co-Supervisor: Mukhamet Nurpeiissov, M.Sc. Student (2nd year), Co-Supervisor: Prof. Tohid Alizadeh, Thesis: "\textbf{Robot Learning and human-robot interaction framework based on programming by demonstration}" (currently Data Scientist, Institute of Smart Systems and Artificial Intelligence, Nazarbayev University)\vspace{0.5cm}
    \item \textcolor{teal}{Superved more than 14 undergraduate students formally through graduation projects or informally interested in working with me. Most of these supervised projects led to the 13 different publications either in journals and conferences in the field of Brain-Computer Interfaces}.\vspace{0.5cm}    
\end{itemize}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\renewcommand{\refname}{Patents}
%
%\begin{thebibliography}{10}
%\small
%\bibitem{p1}
% J.~An, S.H.~Jin, S.H.~Lee, J.I.~Moon  \underline{B. Abibullaev}, J.H.~Ahn and G.H. Jang.
%\newblock REHABILITATION TRAINING SYSTEM AND METHOD.
%\newblock {\em U.S. Patent No}: 9,081,890,Washington, DC: United States. Patent and Trademark Office, 2015 (https://www.google.com/patents/US9081890).
%%------------------------------
%\bibitem{p2}
% J.~An, S.H.~Jin, S.H.~Lee, J.I.~Moon  \underline{B. Abibullaev}, J.H.~Ahn and G.H. Jang.
%\newblock Self-directed rehabilitation training method combining brain signals and functional electrostimulation.
%\newblock {\em EFS ID}: 17077057, {\em Application number}: 14049302, 09-OCT-2013, United States, (http://www.google.com/patents/US20140200632).
%\end{thebibliography}
%\vspace{10pt}
%%-------------------------------------------------------------------------
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\renewcommand{\refname}{Manuscripts - submitted} %Refereed Journal Publications
%\label{publications}
%\begin{thebibliography}{10}
%    
%\small
%\bibitem{h2a}
%\underline{B. Abibullaev} et al.
%\newblock A Systematic Deep Learning Model Selection for P300-Based Brain-Computer Interfaces
%\newblock \textit{IEEE Transactions on Systems, Man and Cybernetics: Systems}, submitted, October, 2019.
%   
%\bibitem{aP2014}
%\underline{B. Abibullaev} et al.
%\newblock A CNN Model Selection for Subject-Independent P300-Based BCIs.
%\newblock {\em IEEE Signal Processing Letters}, submitted, November, 2019.    
%\end{thebibliography}
%\vspace{10pt}

%\section{References}
%\cventry{}{\small Hee-Don Seo Ph.D}{}{}{}{
%{
%\begin{itemize}
%\item[] Professor Emeritus, \\
%Department of Electronic Engineering, Yeungnam University,\\
%Dae-dong 214-1, Gyeongsan, 712-749, South Korea.\\
%Email: \href{mailto:hdseo@ynu.ac.kr}{hdseo@ynu.ac.kr}
%\end{itemize}
%}}
%\vspace{0.5cm}
%\cventry{}{\small Yakov Familiant Ph.D}{}{}{}{
%   {
%       \begin{itemize}
%           \item[]  
%           Eaton Corporation,\\
%           Milwaukee WI, USA \\
%           Innovation Center, PSA group,\\
%           Email: \href{mailto:familiant@gmail.com}{familiant@gmail.com}
%       \end{itemize}
%}}
%
%\vspace{0.5cm}
%\cventry{}{\small Siamac Fazli Ph.D}{}{}{}{
%   {
%       \begin{itemize}
%           \item[] Associate Professor,
%           \item[] School of Science and Technology,\\
%           Nazarbayev  University,\\
%           53 Kabanbay batyr Ave, Astana,\\
%           Republic of Kazakhstan, 010000.\\
%           Email: \href{mailto:vassilios.tourassis@nu.edu.kz}{vassilios.tourassis@nu.edu.kz}
%       \end{itemize}
%}}
%\vspace{0.5cm}
%\cventry{}{\small Jose Luis Contreras-Vidal, Ph.D}{}{}{}{
%{
%\begin{itemize}
%\item[] Professor, \\
%Dept. of Electrical \& Computer Engineering\\
%N308 Engineering Bldg 1\\
%4726 Calhoun Rd\\
%Houston, TX, USA, 77004-4005\\
%Email: \href{mailto: jlcontreras-vidal@uh.edu}{ jlcontreras-vidal@uh.edu}
%\end{itemize}
%}}
%
%\vspace{0.5cm}
%\cventry{}{\small Jinung An Ph.D.}{}{}{}{
%{
%\begin{itemize}
%\item[] Robotics Research Division,\\
%Daegu Gyeongbuk Institute of Science and Technology,\\
%333 Junang-daero, Hyeongpung-myeon, Daegu, 711-873, South Korea.\\
%Email: \href{mailto:robot@dgist.ac.kr}{robot@dgist.ac.kr}
%\end{itemize}
%}}



%\vspace{0.5cm}
%\cventry{}{\small Seung Bong Hong M.D., Ph.D}{}{}{}{
%{
%\begin{itemize}
%\item[] Professor \& Director of Epilepsy Center,\\
%Samsung Medical Center,\\
%Department of Neurology, Sungkyunkwan University School of Medicine,\\
%81 Irwon-Ro Gangnam-gu, 135-710, Seoul, Korea.\\
%Email: \href{mailto:sbhong@skku.edu}{sbhong@skku.edu}
%\end{itemize}
%}}
\vspace{0.5cm}
\end{document}